An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-14 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text

Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational and physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering 
of services and applications for CPS~\cite{Metzger2014}. Important quality aspects for CPS include scalability, 
e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI} \textcolor{red}{only scalability?}.
Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, 
rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.

@@

%----------------------------------------------------------------------------------------------
\subsection{Stand-alone PV System Optimization Technique}
%----------------------------------------------------------------------------------------------
In order to recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables. As number of optimization variables increases, the computation effort will increase as well. Hence, to obtain the best PV system design as well as simplified sizing process, prior work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical methods~\cite{Alsadi2018} \textcolor{red}{why [6]? Alessandro: Não entendi o 6 aqui}.

@@

\subsection{Assumptions and Premises}
Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to the code in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect the technical information. Moreover, the price of each item \textcolor{red}{was obtained from available quotation of the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars) MUDEI O TEXTO POIS A CONSULTA NA WEB P/ OBTER PREÇO DEMANDOU VÁRIOS SITES}.

@@

Regarding financial analysis:
\begin{itemize}
	\item LCC lifetime considered: 20 years;
	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost~\cite{Agrener2013};
%	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013]. Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}. This cost includes the battery lifetime (4 years for lead-acid batteries). Therefore will be performed three battery bank replacements during the LCC analysis.
\end{itemize}

@@

We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification). \textcolor{red}{These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{Agrener2013}}.

>>>>

Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational and physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. 
%Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI} \textcolor{red}{only scalability?}.
Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.

@@

%----------------------------------------------------------------------------------------------
\subsection{Stand-alone PV System Optimization Technique}
%----------------------------------------------------------------------------------------------
In order to recommend an optimal configuration for PV systems, the designer has to evaluate the design based on optimization variables. As number of optimization variables increases, the computation effort will increase as well. Hence, to obtain the best PV system design as well as simplified sizing process, prior work introduced three main techniques for system sizing calculation, namely intuitive, numerical, and analytical \textcolor{red}{methods~\cite{Zhou2010}}.

@@

\subsection{Assumptions and Premises}
Regarding the line 2 of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to the code in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect the technical information. Moreover, the price of each item \textcolor{red}{was obtained from available quotation of the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. MUDEI O TEXTO POIS A CONSULTA NA WEB P/ OBTER PREÇO DEMANDOU VÁRIOS SITES}

@@

Regarding financial analysis:
\begin{itemize}
	\item LCC lifetime considered: 20 years;
	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost~\cite{Agrener2013};
%	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013]. Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}. This cost includes the battery replacement based on its lifetime (4 years for lead-acid batteries). Therefore will be performed three battery bank replacements during the LCC analysis.
\end{itemize}

@@

We have performed seven stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first column of Table~\ref{tab1} (named Specification). \textcolor{red}{These case studies where defined based on usual electrical load found in riverside communities of Amazon State in Brazil~\cite{abs-1811-09438, Agrener2013}}.
